---
title: "basic-pass-at-k"
output: pdf_document
date: "2022-08-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```

## Basic Pass at K Calculation

Goal of this R file is to read in the data from ``all-pass-at-l-eval-run.csv``
and plot it according to language and to sublanguage. Exact plot types are 
not at all final, but the idea is to do a first pass at reading in the data.

```{r load-pass-1}
frequency_map <- read_csv("frequency-map.csv", col_names = c('PL','FREQ'))
cn<- c("PL","MODEL","TEMP","DOCS","TERMS","MIN_COMPLETE","K","MIN_PROBLEM","RES")
pass_at_1 <- read_csv("../model_results/all-pass-at-1-eval-run.csv",col_names = cn)
pass_at_1 <- pass_at_1 %>% mutate(EXPT = paste0(DOCS,'_',TERMS))
pass_at_1 <- merge(pass_at_1,frequency_map)
```

```{r load-pass-1}
pass_at_10 <- read_csv("../model_results/all-pass-at-10-eval-run.csv",col_names = cn)
pass_at_10 <- pass_at_10 %>% mutate(EXPT = paste0(DOCS,'_',TERMS))
pass_at_10 <- merge(pass_at_10,frequency_map)

pass_at_100 <- read_csv("../model_results/all-pass-at-100-eval-run.csv",col_names = cn)
pass_at_100 <- pass_at_100 %>% mutate(EXPT = paste0(DOCS,'_',TERMS))
pass_at_100 <- merge(pass_at_100,frequency_map)

all_pass <- rbind(pass_at_1,rbind(pass_at_100,pass_at_10))
```

```{r}
per_problem <- read_csv("../results/per_problem_pass.csv",col_names = c("PL","PROBLEM","MODEL","EXPT","rate1","rate10","rate100"))
per_problem <- merge(per_problem,frequency_map)
per_problem$rate1 <- as.numeric(per_problem$rate1)
per_problem$rate10 <- as.numeric(per_problem$rate10)
per_problem$rate100 <- as.numeric(per_problem$rate100)
```

```{r load-at-10}
cn<- c("PL","MODEL","TEMP","DOCS","TERMS","MIN_COMPLETE","K","MIN_PROBLEM","RES10")
pass_at_10 <- read_csv("~/polyglot-codegen-evaluation/model_results/all-pass-at-10-eval-run.csv", col_names = cn)



#pass_results<- tibble::add_column(pass_at_1, pass_at_10$RES10)

#pass_results<- dplyr::rename(pass_results, RES10 = `pass_at_10$RES10`)

#remove unneeded columns
#pass_results %>% dplyr::select(-c(MIN_COMPLETE, MIN_PROBLEM, K))

#make a davinci only data set 
davinci_only <- dplyr::filter(pass_at_1, pass_at_1$MODEL == 'davinci')
```

As a first pass, let's just plot all of the versions of the Python runs, 
which are arguably relatively simple to handle

```{r only-python}
# python_only <- dplyr::filter(pass_results, (pass_results$PL == "py"))
# print(python_only)
# ggplot(python_only, aes(x=DOCS, y=RES, col=factor(MODEL))) + geom_point()+ geom_point(data=python_only,aes(DOCS, RES10)) + facet_grid(~ TERMS, scales = 'free') + theme_bw() + ylab("Pass@k") + xlab("Variation")
```

Plot only JavaScript versus TypeScript on Davinci:
```{r js_v_ts}
js_v_ts <- dplyr::filter(davinci_only, (davinci_only$PL == "js" | davinci_only$PL == "ts"))
ggplot(js_v_ts, aes(x=DOCS, y=RES, col=factor(PL))) +
  ylab("Pass at K Rate") + xlab("Variation") +
  geom_point()  +
  facet_grid(~ TERMS, scales = 'free') + theme_bw() + ylab("Pass@k") + xlab("Variation")
```

Plot all languages on Davinci 0.2:
```{r everything}
ggplot(davinci_only, aes(x=DOCS, y=RES, col=factor(PL))) +  
  ylab("Pass at K Rate") + xlab("Variation") +
  geom_point() +
  facet_grid(~ TERMS, scales = 'free') +  theme_bw() + ylab("Pass@k") + xlab("Variation")
```

Plot pass at 1 by model and experiment, Python-only

```{r}
ggplot(subset(pass_at_1,PL=="py"),aes(x=EXPT,y=RES,fill=MODEL)) + geom_col(position="dodge")
```

Plot pass at 1 by model, expt=KEEP KEEP, languages by frequency
 
```{r}
pl_labs <- c(`cpp` = "C++", `java` = "Java", `js` = "JavaScript", `py` = "Python",`pl` = "Perl", `r` = "R", `rs` = "Rust", `scala` = "Scala",`swift` = "Swift", `cs` = "C#", `php` = "PHP", `rb` = "Ruby",`d` = "D", `jl` = "Julia", `lua` = "Lua", `rkt` = "Racket", `ts` = "TypeScript")
pass_at_1$FREQ <- factor(pass_at_1$FREQ,levels = c("High","Medium","Low","Niche"))
ggplot(subset(pass_at_1,EXPT=='transform_transform'),aes(x=PL,y=RES,fill=MODEL)) + geom_col(position="dodge") + scale_x_discrete(name ="Language", labels=pl_labs)+ facet_wrap(~FREQ, nrow = 4,scales = "free_x") + ylab("Pass@1 rates") + theme(text=element_text(size=16))
ggsave("lang_freq_pass1_reworded.pdf")
```

Plot all passes, by model and language for all experiments

```{r}
all_pass$K <- factor(all_pass$K,levels = c("1","10","100"))
all_pass <- all_pass %>% mutate(MODEL_K = paste0(MODEL,'_',K))
all_pass$MODEL_K <- factor(all_pass$MODEL_K,levels = c("davinci_1","davinci_10","davinci_100","incoder_1","incoder_10","incoder_100"))
ggplot(all_pass, aes(x=PL,y=RES,fill=MODEL_K)) + geom_col(position="dodge") + scale_x_discrete(name ="Language", labels=pl_labs)+ facet_wrap(~EXPT, nrow = 4) + scale_fill_manual(name = "Model", values=c("#DC267F", "#FE6100", "#FFB000","#000000","#0072B2","#56B4E9"),labels=c('Codex k=1', 'Codex k=10','Codex k=100','InCoder k=1', 'InCoder k=10','InCoder k=100')) + ylab("Average pass rate")+ theme(text=element_text(size=16))
ggsave("all_models_temps.pdf")
```

Plot all passes, by model and language for TRANSFORM TRANSFORM

```{r}
ggplot(subset(all_pass,EXPT="transform_transform"), aes(x=PL,y=RES,fill=MODEL_K)) + geom_col(position="dodge") + scale_x_discrete(name ="Language", labels=pl_labs) + scale_fill_manual(name = "Model", values=c("#DC267F", "#FE6100", "#FFB000","#000000","#0072B2","#56B4E9"),labels=c('Codex k=1', 'Codex k=10','Codex k=100','InCoder k=1', 'InCoder k=10','InCoder k=100')) + ylab("Average pass rate")  + theme(text=element_text(size=16),axis.text.x = element_text(angle = 90, hjust=1))
ggsave("all_models_temps_reworded.pdf",height=3,width=12)
```

Boxplots using per-problem k=1

```{r}
s <- subset(per_problem,EXPT=='reworded'&MODEL=='davinci')
ggplot(data=na.omit(s), aes(x=PL,y=rate1)) + geom_boxplot(stat = "boxplot",outlier.fill = NULL, outlier.shape = 19, outlier.size = 1.5) 
```

```{r}
s <- subset(per_problem,EXPT=='reworded'&MODEL=='davinci')
ggplot(data=na.omit(s), aes(x=PL,y=rate1)) + geom_violin() + geom_jitter(height = 0, width = 0.1)
```


```{r}
ggplot(data=na.omit(s), aes(x=factor(PROBLEM),y=rate1)) + geom_jitter(height = 0, width = 0.1)
```


## Do Some High Level Stats 

```{r frequency}
category_data <- dplyr::left_join(davinci_only, frequency_map)
```

